\cvsection{Experience}

\begin{cventries}

  \cventry
    {Software Developer} % Job title
    {Sylo} % Organization
    {Auckland, New Zealand} % Location
    {Nov. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Independently developed a replacement for the Sylo node written entirely in \textbf{Rust}, powered by \textbf{websockets}, http, cryptographic signatures, and Ethereum smart contracts.}
        \item {Manage and develop a Discord Bot to assign roles based on owned NFT's, powered by \textbf{Wallet Connect} and \textbf{Serenity}.}
      \end{cvitems}
    }

  \cventry
    {Club President \& Founding Member} % Job title
    {Google Developer Student Club} % Organization
    {Auckland, New Zealand} % Location
    {Aug. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Liaised with Google representatives and oversaw the club's operations.}
        \item {Organised, hosted, and spoke at a machine learning workshop with 100+ attendees.}
      \end{cvitems}
    }

  \cventry
    {Software Developer} % Job title
    {University of Auckland} % Organization
    {Auckland, New Zealand} % Location
    {Nov. 2021 - Feb. 2022 (4 mos)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed and developed a \textbf{REST Api} to generate audio files from provided text, powered by \textbf{Festival} and \textbf{Flite}.}
        \item {Wrote a rate limiting framework to prevent abuse of the API by individual user accounts.}
      \end{cvitems}
    }


  \cventry
    {CAD Draughtsman} % Job title
    {Blue Barn Consulting} % Organization
    {Auckland, New Zealand} % Location
    {Jan. 2019 - Jun. 2021 (2yrs 6mos)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a dashboard to show the onsite status of employees, working within an embedded environment with limited compute resources}
        % \item {Completed CAD Drawings to a high standard, including the use of AutoCAD, Civil3D, and Vehicle Tracking}
        \item {Developed \textbf{AutoHotKey} scripts to improve efficiency of drafting, championed rolling these out to other drafters}
        \item {Prototyped a tool to automate the generation of reports, increasing the efficiency of engineers.}
      \end{cvitems}
    }

%   \cventry
%     {Software Engineer Intern} % Job title
%     {Toast} % Organization
%     {Auckland, New Zealand} % Location
%     {Jan. 2017 - Aug. 2017} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Built a microservice, database schema, and related web pages to manage customer accounts --- 50,000+ created within the first two months.}
% 		\item {Designed and helped implement a second microservice as a month-long architecture refactor to reduce technical debt and build the infrastructure for upcoming payment features.}
% 		\item {Enhanced the audit tool to query real-time data from restaurants' Android devices, proactively resolving customers' configuration bugs.}
%       \end{cvitems}
%     }

\end{cventries}
