\cvsection{Experience}

\begin{cventries}
  \cventry
    {Software Engineer II}
    {Partly}
    {Christchurch, New Zealand}
    {Aug. 2023 - Present}
    {
      \begin{cvitems}
        % Dismantler API
        % Parts Interpretation API
        % Managed Dependency upgrades
        % Developed automated tooling to lint custom configuration files in the monorepo.
        \item {Designed and built the REST API behind Partly's dismantler platform, servicing 1000s of requests per day over 6 months.}
        \item {Managed a team of 3 developers to build a Vehicle API capable of generating a graph of all parts in a vehicle given only a VIN over 6 months.}
        \item {Developed a tool to automatically lint custom configuration files in the monorepo, reducing outages from misconfiguration by 100\% over the course of 2 months.}
        \item {Upgraded in excess of 1000 dependencies, bringing the entire monorepo up four major NodeJS versions, two major Ubuntu versions, and major versions of dozens of NodeJs and Rust dependencies over the course of 4 months.}
        \item {Worked with \textbf{Rust}, \textbf{Axum}, \textbf{Kubernetes}, \textbf{Bash}, \textbf{Kafka}, \textbf{Postgres}, and \textbf{Scylla} while at Partly.}
      \end{cvitems}
    }

  \cventry
    {Software Engineering Intern}
    {Crown Equipment RTC}
    {Auckland, New Zealand}
    {Nov. 2022 - Aug. 2023}
    {
      \begin{cvitems}
        \item {Developed a \textbf{simulation engine} powered by \textbf{GPU Acceleration} to validate forklift control software in a fully simulated environment.}
        \item {Used \textbf{Python} to develop a variety of \textbf{CLI tools} and logging utilities to improve developer efficiency.}
      \end{cvitems}
    }

  \cventry
    {Software Developer} % Job title
    {Sylo} % Organization
    {Auckland, New Zealand} % Location
    {Nov. 2021 - Nov. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Independently developed a replacement for the Sylo node written entirely in \textbf{Rust}, powered by \textbf{websockets}, http, cryptographic signatures, and Ethereum smart contracts.}
        \item {Manage and develop a Discord Bot to assign roles based on owned NFT's, powered by \textbf{Wallet Connect} and \textbf{Serenity}.}
      \end{cvitems}
    }

  \cventry
    {Club President \& Founding Member} % Job title
    {Google Developer Student Club} % Organization
    {Auckland, New Zealand} % Location
    {Aug. 2020 - Nov. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Liaised with Google representatives and oversaw the club's operations.}
        \item {Organised and presented a machine learning workshop with 100+ attendees.}
        \item {Organised a Hackathon with 60 attendees in collaboration with the DEVs society.}
      \end{cvitems}
    }

  \cventry
    {Software Developer} % Job title
    {University of Auckland} % Organization
    {Auckland, New Zealand} % Location
    {Nov. 2021 - Feb. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed and developed a \textbf{REST Api} to generate audio files from provided text, powered by \textbf{Festival} and \textbf{Flite}.}
        \item {Developed a robust testing framework to ensure the API is performing within spec, including benchmarking for performance metrics.}
        \item {Wrote a rate limiting framework to prevent abuse of the API by individual user accounts.}
      \end{cvitems}
    }


  % \cventry
  %   {CAD Draughtsman} % Job title
  %   {Blue Barn Consulting} % Organization
  %   {Auckland, New Zealand} % Location
  %   {Jan. 2019 - Jun. 2021 (2yrs 6mos)} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Developed a dashboard to show the onsite status of employees, working within an embedded environment with limited compute resources}
  %       % \item {Completed CAD Drawings to a high standard, including the use of AutoCAD, Civil3D, and Vehicle Tracking}
  %       % \item {Developed AutoHotKey scripts to improve efficiency of drafting, championed rolling these out to other drafters}
  %       \item {Prototyped a tool to automate the generation of reports, increasing the efficiency of engineers.}
  %     \end{cvitems}
  %   }

%   \cventry
%     {Software Engineer Intern} % Job title
%     {Toast} % Organization
%     {Auckland, New Zealand} % Location
%     {Jan. 2017 - Aug. 2017} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Built a microservice, database schema, and related web pages to manage customer accounts --- 50,000+ created within the first two months.}
% 		\item {Designed and helped implement a second microservice as a month-long architecture refactor to reduce technical debt and build the infrastructure for upcoming payment features.}
% 		\item {Enhanced the audit tool to query real-time data from restaurants' Android devices, proactively resolving customers' configuration bugs.}
%       \end{cvitems}
%     }

\end{cventries}
